---
title: "Test notebook"
author: "Bbm"
date: "7/26/2021"
output: pdf_document
---

# **Introduction**
This is a model built on the Kaggle Video Game Sales dataset which was created in 2016. 

The data consists of 16719 records of video games along with their Year released, Genre, Publisher, Platform, and total sales data for North America, European Union, Japan, and other countries. 

# **Methods/analysis**

## Initial Set up

Let's install tidyverse and import data.

```{r echo=FALSE}
library(tidyverse)
library(readr)
Video_Games_Sales_as_at_22_Dec_2016 <- read_csv("Kaggle_Video_Game_Sales_Data/Video_Games_Sales_as_at_22_Dec_2016.csv")
View(Video_Games_Sales_as_at_22_Dec_2016)
Data<-Video_Games_Sales_as_at_22_Dec_2016
```

Let's create the training and test sets for determining overall sales. Here I used the standard division of 80% training, 20 % test.

```{r}
library(caret)
set.seed(0623)
test_index <- createDataPartition(Data$Global_Sales, times = 1, p = 0.8, list = FALSE)
test_set <-  Orig_Data[test_index, ] 
train_set <- Orig_Data[-test_index, ]
```

## Exploratory Data Analysis

## Model Creation

For this project I'll use two models: basic linear regression (which was suggested by the Kaggle website), as well as a Regression tree model.

Let's start with basic regression. 

```{r}
library(caret)
lm_data<-train_set %>% select(Global_Sales,Genre,Platform,Critic_Score,Critic_Count,User_Count,User_Count)
train_lm <-train(Global_Sales ~ ., method='lm', data=train_set,na.action = na.pass)
```

# Results

# Further thoughts
